% !TEX encoding = UTF-8
% !TEX program = pdflatex
% !TEX spellcheck = it_IT

\documentclass[english,a4paper]{europasscv}
\usepackage[english]{babel}
\usepackage{comment}
\usepackage{lastpage}
\usepackage{hyperref}
\usepackage{fontawesome5}

\ecvname{Olla Gabriele}


\begin{document}

\begin{europasscv}

\ecvtitle{Name}{{{\LARGE Gabriele Olla}}}
\vspace{0.2cm}
\ecvitem{Date of Birth}{17/02/1995}
\ecvitem{Nationality}{Italian}
\ecvitem{Email}{\href{mailto:jobs@ollaw.xyz}{jobs@ollaw.xyz} \href{mailto:ollagabriele@proton.me}{ollagabriele@proton.me}}
\ecvitem{Links}{ \textcolor{ecvrulecolor}{\faLinkedin} \href{https://linkedin.com/in/ollagabriele}{ollagabriele} \quad \textcolor{ecvrulecolor}{\faGitlab} \href{https://gitlab.com/ollaww}{ollaww} \quad \textcolor{ecvrulecolor}{\faGithub} \href{https://github.com/ollaw}{ollaw}}

\ecvsection{Work Experience}

\ecvtitle{May 2022 – Present}{Site Reliability Engineer}
\ecvitem{Company}{\textbf{Prima Assicurazioni}, Milan [\textit{Remote}]}
\ecvitem{Main responsibilities}{%
  \begin{ecvitemize}
    \item Design and management of AWS infrastructure using Pulumi and Terraform.
    \item Introduction of HashiCorp Vault as centralized secret manager.
    \item Okta integration with internal tools (GitHub, Vault, Datadog, RabbitMQ).
    \item Maintenance of CI/CD infrastructure with GitHub Actions and support to development teams.
    \item Migration of RabbitMQ clusters and cloud cost optimization.
  \end{ecvitemize}
}
\vspace{0.2cm}

\ecvtitle{Sep 2021 – May 2022}{Cloud Engineer}
\ecvitem{Company}{\textbf{DXC Technology}, Cernusco sul Naviglio (MI) [\textit{Hybrid}]}
\ecvitem{Main responsibilities}{%
  \begin{ecvitemize}
    \item Provisioning of Kubernetes clusters based on MKE and RKE.
    \item Infrastructure creation on OpenStack using Terraform.
    \item Automated VM configuration via Ansible.
  \end{ecvitemize}
}
\vspace{0.2cm}

\ecvtitle{Mar 2020 – Aug 2021}{Cloud Engineer}
\ecvitem{Company}{\textbf{Storm Reply}, Turin [\textit{Hybrid}]}
\ecvitem{Main responsibilities}{%
  \begin{ecvitemize}
    \item Management and scaling of Jenkins on Kubernetes for CI/CD pipelines.
    \item AWS migrations with infrastructure provisioning via CloudFormation and Terraform.
    \item Application deployment on EKS and EC2 (Linux/Windows) using CodeDeploy.
    \item Setup and configuration of an ELK stack for centralized monitoring.
  \end{ecvitemize}
}
\vspace{0.2cm}

\ecvsection{Certifications}

\ecvitem{Linux Foundation, 2025}{FinOps Certified Engineer}
\ecvitem{HashiCorp, 2025}{HashiCorp Certified: Vault Associate (003)}
\ecvitem{Linux Foundation, 2023}{Certified Kubernetes Security Specialist (CKS)}
\ecvitem{Linux Foundation, 2021}{Certified Kubernetes Application Developer (CKAD)}
\ecvitem{Linux Foundation, 2021}{Certified Kubernetes Administrator (CKA)}
\ecvitem{AWS, 2021}{AWS Solution Architect (SAA-CO2)}

\ecvsection{Education}

\ecvtitlelevel{2017 – 2020}{Master’s Degree in Computer Science and Technologies}{ISCED~7}
\ecvitem{}{\textit{University of Turin}}
\ecvitem[.2cm]{Final Grade}{110/110 cum laude}
\ecvitem{Thesis}{Identity and Access governance: managing digital identities within a company.}

\ecvtitlelevel{2014 – 2017}{Bachelor’s Degree in Computer Science and Technologies}{ISCED~6}
\ecvitem{}{\textit{University of Turin}}
\ecvitem[.2cm]{Final Grade}{110/110 cum laude}
\ecvitem{Thesis}{Vulnerability assessment of Android applications: a tool for automation.}

\ecvsection{Technical Skills}

\ecvblueitem{Cloud Computing}{Extensive experience in designing and managing infrastructures on Amazon Web Services (AWS), with a focus on scalability, security, and cost optimization. Responsible for managing multi-account environments with centralized organizational structures and fine-grained access control. Advanced proficiency with Infrastructure as Code (IaC) tools such as Pulumi and Terraform.}

\ecvblueitem{IAM \& Secrets Management}{Led the introduction and management of complex IAM solutions in enterprise environments. Broad experience integrating Okta as an Identity Provider (IdP) and Single Sign-On (SSO) solution for critical services (AWS, GitHub, Vault, RabbitMQ, Artifactory [...]). Designed and implemented HashiCorp Vault as a centralized secret manager, including policy definition, Kubernetes integration, and secure lifecycle management of secrets.}

\ecvblueitem{Containers \& Orchestration}{Advanced expertise in container and orchestrator management. Provisioning and maintenance of Kubernetes clusters, both managed (EKS) and self-hosted (MKE, RKE), with experience in multi-cluster environments and automated deployment workflows. Workload migrations and integration of external tools such as Vault and Okta.}

\ecvblueitem{Messaging \& Event Systems}{Hands-on experience in managing and migrating RabbitMQ clusters, including federation across environments and configuration management on CloudAMQP in multi-tenant setups. Integration of RabbitMQ with centralized authentication systems and monitoring solutions.}

\ecvblueitem{Tooling \& DevOps}{Management of CI/CD infrastructure using GitHub Actions. Setup and maintenance of feature flagging tools (LaunchDarkly) and observability platforms (Datadog). Experience in pipeline automation, containerized release processes, and implementation of metrics for performance monitoring and optimization.}

\ecvblueitem{Additional Skills}{Good experience with Python, Java, and Kotlin. Basic knowledge of Go and C (including parallel computing with OpenMP/MPI) and JavaScript with frontend experience (React/Vue). Academic experience with Android SDK for mobile development. Strong collaboration skills in distributed teams and proven autonomy in remote work environments.}

\ecvsection{Languages}

\ecvmothertongue{Italian}
\ecvblueitem{Other Languages}{English (C1 – Fluentify Language Assessment, 12/2022)}

\ecvsection{Additional Information}

\ecvblueitem{Driving License}{A, B}
\ecvblueitem{Data Processing Consent}{I authorize the processing of my personal data in accordance with the Italian Legislative Decree no. 196 of June 30, 2003, "Personal Data Protection Code."}

		  
\end{europasscv}

\end{document}

